\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}


\begin{document}

\LARGE{The Disciplined Entrepeneurship}
\Large{Product:-}\\
\Large{Revision:-}\\
\Large{\today}\\

\textbf{1.Raison d'Etre}\\
\textit{Why are you in business?}\\
Mission:\\
Passion:\\
Value:\\
Initial Assets:\\
Initial Idea:\\

\textbf{2.Initial Market}\\
\textit{Who is your customer?}\\
Beachhead:\\
End User Profile:\\
TAM:\\
Persona:\\
First 10 customer:\\

\textbf{3.Value Creation}\\
\textit{What can you do for your customer?}
Use Case:\\
Product Description:\\
Problem Being Solved:\\
Qualified Value Proposition:\\

\textbf{4.Competition Advantage}\\
\textit{Why you?}\\
Moats:\\
Core:\\
Competition Positioning:\\

\textbf{5.Customer Acquisition}\\
\textit{How does your customer acquire your product?}\\
DMU:\\
Process to Acquire Customer:\\
Windows of Opportunity:\\
Possible Triggers:\\

\textbf{6.Product Unit Economics}\\
\textit{Can you make money?}\\
Business Model:\\
Estimated Pricing\\
Short Term LTV:\\
Short Term COCA:\\
Medium Term LTV:\\
Medium Term COCA:\\
Long Term LTV:\\
Long Term COCA:\\

\textbf{7.Sales}\\
\textit{How do you sell your product?}\\
Preferred Sales Channel:\\
Sales Funnel:\\
Short Term Mix:\\
Medium Term Mix:\\
Long Term Mix:\\

\textbf{8.Initial Market}\\
\textit{Who is your customer?}\\
Estimated R\&D Expense:\\
Estimated G\&A Expense:\\
LTV/COCA Ratio High Enough:\\
\newpage
\textbf{9.Design \& Build}\\
\textit{How do you produce your product?}\\
Identify Key Assumption:\\
Test Key Assumption:\\
MVBP:\\
Tracking Metrics\\

\textbf{10.Scaling}\\
\textit{How do you scale your business?}\\
Product Plan for Beachhead:\\
Next Market:\\
Product Plan beyond Beachhead:\\
Follow-on TAM:

\end{document}
